Supplementary Figures: Quality control for the target decoy approach for peptide identification

### 2022-11-13 paper_supplementary.Rmd
comply with achemso template of JPR + add myTemplate.tex

---
title: "Supplementary Figures: Quality control for the target decoy approach for peptide identification"
author: 
  Elke Debrie$^1$
  Milan Malfait$^1$
  Ralf Gabriels$^{2,3}$
  Arthur Declerq$^{2,3}$
  Adriaan Sticker$^{2,3}$
  Lennart Martens$^{2,3}$
  Lieven Clement$^{1,4}$
date: 
  $^1$ Department of Applied Mathematics, Computer Science and Statistics, Ghent University, Ghent, Belgium \newline
  $^2$ VIB-UGent Center for Medical Biotechnology, VIB, Zwijnaarde, Belgium \newline
  $^3$ Department of Biomolecular Medicine, Ghent University, Ghent, Belgium \newline
  $^4$ Corresponding Author$:$ lieven.clement@ugent.be
output: 
  bookdown::pdf_document2:
    keep_tex: yes
    latex_engine: xelatex
    citation_package: natbib
    toc: no
link-citations: yes
bibliography: [biblio.bib]
biblio-style: biochem
linkcolor: blue
urlcolor: blue
citecolor: blue
---

\setcitestyle{super,open={[},close={]}}
\def\citenumfont{}

>>>>

---
title: "Supplementary Figures: Quality control for the target decoy approach for peptide identification"
output: 
  bookdown::pdf_document2:
    template: "myTemp.tex"
    keep_tex: yes
    latex_engine: xelatex
    toc: no
    citation_package: natbib
    includes:
      in_header: authors.tex

documentclass: achemso
classoption: 
  - journal=jprobs
  - manuscript=article

bibliography: [biblio.bib]
linkcolor: blue
urlcolor: blue
citecolor: blue
---

```{r echo=FALSE, warning=FALSE}
if (!tinytex::check_installed("achemso")) tinytex::tlmgr_install("achemso")
if (!tinytex::check_installed("caption")) tinytex::tlmgr_install("caption")
if (!tinytex::check_installed("setspace")) tinytex::tlmgr_install("setspace")
```
